The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-08 paper/ms.tex
gaia

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax. While not all of our targets have \gaia radii, we find that where they do both catalogues have comparable precision, but differ by many sigma. While

>>>>

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax. While not all of our targets have \gaia radii, we find that while there is overall agreement to within a few $\sigma$, the results from stellar modelling are consistently slightly larger than those from \gaia. One star noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling. 
% Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling.
It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax.
